---
title: "DV_RProject1"
author: "Probe, Yudkin, Honganen"
date: "Friday, January 30, 2015"
output: html_document
---

##**Step 1:** Load the required packages and data from the database

```{r}

library("bitops")
library("RCurl")

dfCustomers <- data.frame(eval(parse(text=substring(getURL(URLencode('http://129.152.144.84:5001/rest/native/?query="select * from customers"'), httpheader=c(DB='jdbc:oracle:thin:@129.152.144.84:1521/PDB1.usuniversi01134.oraclecloud.internal', USER='DV_ORDERS', PASS='orcl', MODE='native_mode', MODEL='model', returnFor = 'R', returnDimensions = 'False'), verbose = TRUE), 1, 2^31-1))))


dfOrderDetails <- data.frame(eval(parse(text=substring(getURL(URLencode('http://129.152.144.84:5001/rest/native/?query="select * from order_details"'), httpheader=c(DB='jdbc:oracle:thin:@129.152.144.84:1521/PDB1.usuniversi01134.oraclecloud.internal', USER='DV_ORDERS', PASS='orcl', MODE='native_mode', MODEL='model', returnFor = 'R', returnDimensions = 'False'), verbose = TRUE), 1, 2^31-1))))

dfItems <- data.frame(eval(parse(text=substring(getURL(URLencode('http://129.152.144.84:5001/rest/native/?query="select * from items"'), httpheader=c(DB='jdbc:oracle:thin:@129.152.144.84:1521/PDB1.usuniversi01134.oraclecloud.internal', USER='DV_ORDERS', PASS='orcl', MODE='native_mode', MODEL='model', returnFor = 'R', returnDimensions = 'False'), verbose = TRUE), 1, 2^31-1))))

dfOrders <- data.frame(eval(parse(text=substring(getURL(URLencode('http://129.152.144.84:5001/rest/native/?query="select * from orders"'), httpheader=c(DB='jdbc:oracle:thin:@129.152.144.84:1521/PDB1.usuniversi01134.oraclecloud.internal', USER='DV_ORDERS', PASS='orcl', MODE='native_mode', MODEL='model', returnFor = 'R', returnDimensions = 'False'), verbose = TRUE), 1, 2^31-1))))

```

##**Step 2:** Display the data frames

###Customers Dataframe
```{r}
print(dfCustomers)

```

###Order Details Dataframe
```{r}
print(dfOrderDetails)

```

###Items Dataframe
```{r}
print(dfItems)

```

###Orders Dataframe
```{r}
print(dfOrders)

```

##**Step 3:** Load the library and produce an interesting plot for each dataframe

```{r}
library("ggplot2")
```

###Customers Chart - Customers by State

```{r}


ggplot(dfCustomers, aes(x =CUSTOMER_STATE, y =CUSTOMER_CITY))+geom_bar()
```

###Order Details Chart - Orders by Item

###Items Chart - Price Distribution

###Orders Dataframe - Orders by Month
