---
title: "DV_RProject1"
author: "Probe, Yudkin, Honganen"
date: "Friday, January 30, 2015"
output: html_document
---

##**Step 1:** Load the required packages and data

```{r}

source("../01 Data/Load_Packages.R", echo = TRUE)

source("../01 Data/Load_Data_Frames.R", echo = TRUE)


```

##**Step 2:** Display the data frames

###Customers Dataframe
```{r}

head(dfCustomers)

```

###Order Details Dataframe
```{r}

head(dfOrderDetails)

```

###Items Dataframe
```{r}
head(dfItems)

```

###Orders Dataframe
```{r}
head(dfOrders)

```

##**Step 3:** Produce an interesting plot for each dataframe

###Customers Chart - Customers by State

```{r}

source("../02 Visualizations/Interesting_Customers.R", echo = TRUE)

```

###Order Details Chart - Orders by Item

```{r}

source("../02 Visualizations/Interesting_OrderDetails.R", echo = TRUE)

```

###Items Chart - Price Distribution
```{r}

source("../02 Visualizations/Interesting_Items.R", echo = TRUE)

```


###Orders Chart - Orders by Month
```{r}

source("../02 Visualizations/Interesting_Orders.R", echo = TRUE)

```

##**Step 4:** Query the Database and Generate Specified Plots

```{r}

source("../01 Data/Load_Data_Frames2.R", echo = TRUE)

source("../02 Visualizations/Reproduce_Plots.R", echo = TRUE)

```

